Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-02-07 paper/main.tex
Minor edit

Table~\ref{table:eqcorrespondence} lists the corresponding terms between the
basic analytical expressions and the data-driven model $EQ_4$.  While two of the
inertial terms share the same combinations of variables, the data-driven
expression for aerodynamic lift is very different from its analytical
counterpart, and one portion of the pendulum motion is omitted altogether from
the data-driven models.  The reasons for these differences lie in the nature of
the symbolic regression algorithm, which is designed to return only the most
parsimonious expressions capable of predicting the experimental data at a given
level of accuracy.  Therefore, key physical effects may be represented
numerically by terms that are symbolically different and often much simpler than
their analytical counterparts.  This behavior of automatically separating
distinct dynamical building blocks is one of the most powerful aspects of
symbolic regression.  By sweeping the range of several kinematic and geometric
parameters in the 58 sets of training data, any candidate models that
incorrectly mix or couple two separate physical effects are discarded upon
testing on a data set with different parameters.

>>>>

Table~\ref{table:eqcorrespondence} lists the corresponding terms between the
basic analytical expressions and the data-driven model $EQ_4$.  While two of the
inertial terms share the same combinations of variables, the data-driven
expression for aerodynamic lift is very different from its analytical
counterpart, and one portion of the pendulum motion is omitted altogether from
the data-driven models.  The reasons for these differences lie in the nature of
the symbolic regression algorithm, which is designed to return only the most
parsimonious expressions capable of predicting the experimental data at a given
level of accuracy.  Therefore, key physical effects may be represented
numerically by terms that are symbolically different and often much simpler than
their analytical counterparts.  This behavior of automatically separating
distinct dynamical building blocks is one of the most powerful aspects of
symbolic regression.  By sweeping the range of several kinematic and geometric
parameters in the 58 sets of training data, any candidate models that
incorrectly mix or couple two separate physical effects are discarded when
evaluated on data representing different parameters.
